Designing Types for R, Empirically

### 2020-10-08 paper/main.tex
reformat

\documentclass[acmsmall, screen]{acmart}
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
%\settopmatter{printfolios=true,printccs=true,printacmref=true}

\setcopyright{rightsretained}
\acmPrice{}
\acmDOI{10.1145/3360579}
\acmYear{2020}
\copyrightyear{2020}
\acmJournal{PACMPL}
\acmVolume{3}
\acmNumber{OOPSLA}
\acmArticle{153}
\acmMonth{10}

@@

Our tools are open source and publicly available on GitHub\footnote{
\typetracer: \url{https://github.com/PRL-PRG/propagatr}, \contractr: \url{https://github.com/PRL-PRG/contractr}
},
all results in this paper are reproducible and were submitted for
artifact evaluation.
%
\section{Background} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\documentclass[acmsmall, screen]{acmart}
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
%\settopmatter{printfolios=true,printccs=true,printacmref=true}
\setcopyright{rightsretained}
\acmPrice{}
\acmDOI{10.1145/3360579}
\acmYear{2020}
\copyrightyear{2020}
\acmJournal{PACMPL}
\acmVolume{3}
\acmNumber{OOPSLA}
\acmArticle{153}
\acmMonth{10}

@@

Our tools are open source and publicly available on GitHub\footnote{
\typetracer: \url{https://github.com/PRL-PRG/propagatr}, \contractr:
\url{https://github.com/PRL-PRG/contractr} }.
%
\section{Background} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
